\cvsection{Projects}

\begin{cventries}

  \cventry
  
  {Software Developer}
  {\href{https://github.com/yashsriv/beethoven}{Impossible Foods}}
  {\emph{\texttt{\href{https://github.com/yashsriv/beethoven}{github://yashsriv/beethoven}}}}
  {Mar'2022}
  {
    \begin{cvitems}
    \item Create several middleware interfaces for Impossible Foods
    \item Worked on SFTP servers and transform XML Data into IDOC.
    \item Worked on Critical interfaces of Citi Bank.
    \item Worked on Critical Interfaces of Azure Blob and stable the flow for the interfaces.
    \item Got appreciation from the Manager to complete the deliverables on time during the peak time.
    \end{cvitems}
  }

  \cventry
  {Software Developer}
  {\href{https://github.com/yashsriv/networks-video-stream}{Nike}}
  {Dec'2020}
  {
    \begin{cvitems}
    \item Worked on SAP CPI to create middleware Interfaces and wrote several Groovy Scripts to perform different functions. 
    \item Used SQL queries to fetch the Data from the Backend(S4 HANA).
    \item Used Java nd XSLT mappings to transform the data from format to another.
    \item Use YAML to create custom API's for the customer.
    \end{cvitems}
  }

  \smallcventry
  {Course Project, Computer Architecture}
  {\href{https://github.com/yashsriv/branch-predictor/blob/master/report/main.pdf}{Branch Predictor}}
  {Best Predictor}
  {April'2018}
  {\emph{\texttt{\href{https://github.com/yashsriv/branch-predictor/blob/master/report/main.pdf}{github://yashsriv/branch-predictor}}}}
  {
    \begin{cvitems}
    \item Designed a branch predictor for an intra-class branch prediction
      championship based on the CBP-1 framework in a team of 2.
    \item Created a modified GEHL predictor with an additional loop predictor.
    \item Was adjudged the \textbf{best predictor} amongst all submitted.
    \end{cvitems}
  }

  \smallcventry
  {Course Project}
  {\href{https://github.com/yashsriv/haskell-connect-4}{Connect 4 AI in haskell}}
  {Functional Programming}
  {Jan'2018-April'2018}
  {\emph{\texttt{\href{https://github.com/yashsriv/haskell-connect-4}{github://yashsriv/haskell-connect-4}}}}
  {
    \begin{cvitems}
    \item A GUI based connect 4 AI in haskell.
    \item Had support for various difficulties and the AI was abstracted out in
      order to be able to support any complete knowledge two player game.
    \end{cvitems}
  }

  \smallcventry
  {Course Project, Compiler Design}
  {\href{https://github.com/yashsriv/tango}{tango} \strong{(\emph{golang to x86 assembly})} }
  {}
  {Jan'2018-April'2018}
  {\emph{\texttt{\href{https://github.com/yashsriv/tango}{github://yashsriv/tango}}}}
  {
    \begin{cvitems}
    \item A compiler for go written in go in a team of 3. Compiles from golang
      to x86 assembly.
    \item Supports a subset of the go language including nested pointers, type
      checking, recursion, nested arrays, structs, methods and other common
      programming language features.
    \item Added a new for comprehension syntax as well to golang.
    \end{cvitems}
  }

  \smallcventry
  {Self Project}
  {\href{https://github.com/yashsriv/go-nachos}{go-nachos}}
  {Ported nachOS to golang}
  {Dec'2017}
  {\emph{\texttt{\href{https://github.com/yashsriv/go-nachos}{github://yashsriv/go-nachos}}}}
  {}

  \smallcventry
  {Programming Club}
  {\href{http://pclub.in/project/2016/07/06/smartmirror.html}{Smart Mirror}}
  {Best Applicable Project}
  {Summer'2016}
  {\emph{\texttt{\href{https://github.com/11000011/Smart-Mirror}{github://11000011/Smart-Mirror}}}}
  {
    \begin{cvitems}
    \item Built an \textbf{IoT Mirror} with an RPi and a display fitted with a 75\%
      reflecting mirror.
    \item The mirror had features such as weather forecast, calendar
      and pushbullet notifications of a user (determined via face
      identification).
      \item I was involved in integrating Google Calendar notifications and Face
        Identification using Microsoft’s Project Oxford API.
    \item Received \textbf{Best Applicable Project} amongst all summer projects under
      the Science and Technology Council, IIT Kanpur.
    \end{cvitems}
  }

  \smallcventry
  {Association of Computing Activities}
  {\href{https://github.com/yashsriv/Reversi-Python}{Reversi Game in Python}}
  {IIT Kanpur}
  {2\textsuperscript{nd} Semester}
  {\emph{\texttt{\href{https://github.com/yashsriv/Reversi-Python}{github://yashsriv/Reversi-Python}}}}
  {
    \begin{cvitems}
    \item Developed a Python Application using \textbf{Pygame} for 2 player as well as
      single player Reversi gameplay.
    \item Uses the \textbf{negamax algorithm} with an efficient heuristic check
      for better performance against humans.
    \item Mid Semester project under the Association of Computing Activities (ACA), IIT Kanpur.
    \item Link: \href{https://github.com/yashsriv/Reversi-Python}{github.com/yashsriv/Reversi-Python}
    \end{cvitems}
  }

  \cventry
  {Member, Team Robocon IIT Kanpur\ifdefined\ONEPAGE\else, Prof. Bhaskardas Gupta\fi}
  {ABU Robocon 2016}
  {IIT Kanpur}
  {Oct'2015 - Mar'2016}
  {
    \begin{cvitems}
      \item An autonomous robot, which did not contain a driving actuator had to
        traverse a game field using energy provided to it by another robot in
        form of a non contact force.
      \item Was involved in \textbf{Image Processing} used in the autonomous
        robot for \textbf{color detection} and \textbf{line following}
        \ifdefined \ONEPAGE \else to traverse the arena. \fi
      \item Came \textbf{3\textsuperscript{rd}} out of 105 teams in Nationals at Pune, India.
    \end{cvitems}
  }

  \smallcventry
  {24 Hour Hackathon}
  {Code.Fun.Do}
  {Microsoft India}
  {Sept'2015}
  {Best 5 ideas}
  {
    \begin{cvitems}
    \item Developed an App to help connect teachers and learners based on their
      preference of subjects.
    \item Used cross-platform \textbf{Universal App Platform} for Windows 10
      and a server written in C\#.
    \item Was selected as one of the \textbf{best five ideas}.
    \end{cvitems}
  }

\end{cventries}
\vspace{-2mm}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../cv.tex"
%%% TeX-engine: xelatex
%%% End:
